Paper figures

### 2019-06-20 voltagebudget/analysis/paper_figures_redraft.Rmd
Add dianostic plots for opt exps

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(readr)
library(gridExtra)
library(readr)

@@

@@

# --------------------------------------------------------------------
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
exps <- c(82, 83, 84, 85)

@@

# Load exp spikes
exps <- c(86, 87, 88, 89)
fig4 <- NULL
for (n in 1:4){
  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
  df$set <- rep("synchronized", nrow(df))

@@

# Data
exp <- "104"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

@@

exp <- "105"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

@@

fig15$alg <- rep("max", nrow(fig15))
fig16$alg <- rep("uniform", nrow(fig16))
fig17 <- rbind(fig15, fig16)
# --------------------------------------------------------------------
rm(df, exp, freq, freqs, name, ref, n, sigmas, sigma, exps, alg_names, algs)
```

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=.8, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
  theme_classic() -> p7

print(summary(fig2_ratios$ratio))
fig2_ratios %>% 
  ggplot(aes(x=freq, y=ratio)) +
  geom_point(color="darkslategray3", size=1.6) +
  xlab("Freq (Hz)") +
  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
  theme_classic() +
  ylim(0, 1) -> p8

@@

# Optimal derivation
```{r, fig.width=1.3, fig.height=2}
min_t <- min(fig4$ts)

fig4 %>% 
  filter(alg != "coincidence", alg != "left") %>% 
  group_by(set, alg) %>% 
  mutate(ts = ts - min_t) -> tmp

tmp %>% 
  filter(set == "synchronized") %>%
  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
  geom_point(size=2, alpha=1, shape=4) +
  geom_point(
    data=filter(tmp, set == "initial"),
    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.2) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

fig3 %>% 
  filter(alg != "coincidence", alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=0.6, alpha=0.99) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
  theme_classic() +
  coord_flip() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="bottom",
    legend.key.size = unit(.2, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

@@

```{r, fig.width=1.1, fig.height=3}
ms <- 1e3

fig17 %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=.2) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
  labs(x="Variance (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  theme_classic() +
  theme(legend.position="bottom",
    legend.key.size = unit(.2, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) 
```

>>>>

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(readr)
library(gridExtra)
library(readr)
library(NNTbiomarker)

@@

find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}

@@

# --------------------------------------------------------------------
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
exps <- c(114, 115, 116, 117)

@@

# Load exp spikes
exps <- c(110, 111, 112, 113)
fig4 <- NULL
for (n in 1:4){
  # df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_target0.01_spikes.csv", sep=""))
  df$set <- rep("synchronized", nrow(df))

@@

# Data
exp <- "118"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

@@

exp <- "119"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

@@

# -
exp <- "109"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

fig18 <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  # df %>%
    # filter(n_spikes_pop > 0) -> df

  df$freq <- rep(freq, nrow(df))
  fig18 <- rbind(fig18, df)
}

# -
fig15$alg <- rep("max", nrow(fig15))
fig16$alg <- rep("uniform", nrow(fig16))
fig18$alg <- rep("coincidence", nrow(fig18))
fig17 <- rbind(fig15, fig16, fig18)
# --------------------------------------------------------------------
rm(df, exp, freq, freqs, name, ref, n, sigmas, sigma, exps, alg_names, algs)
```

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=.8, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black")) -> p7

print(summary(fig2_ratios$ratio))
fig2_ratios %>% 
  ggplot(aes(x=freq, y=ratio)) +
  geom_point(color="darkslategray3", size=1.6) +
  xlab("Freq. (Hz)") +
  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
  theme_classic() +
  ylim(0, 1) -> p8

@@

# Optimal derivation
```{r, fig.width=1.3, fig.height=2.2}
min_t <- min(fig4$ts)

fig4 %>% 
  filter(alg != "left") %>% 
  group_by(set, alg) %>% 
  mutate(ts = ts - min_t) -> tmp

tmp %>% 
  filter(set == "synchronized") %>%
  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
  geom_point(size=2.3, alpha=1, shape=4) +
  geom_point(
    data=filter(tmp, set == "initial"),
    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.2) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

fig3 %>% 
  filter(alg != "left") %>%
  filter(obs_variances > 10e-3) %>% 
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  # geom_line(size=0.1, alpha=0.99) +
  geom_point(size=1, alpha=0.99) +
  scale_color_manual("Algorithm:", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  theme_classic() +
  coord_flip() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="bottom",
    legend.key.size = unit(.2, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

@@

```{r, fig.width=3, fig.height=2.8}

hospital_names <- list(
  '8'="Freq.\n\n8 Hz",
  '12'="12 Hz",
  '20'="20 Hz",
  '30'="30 Hz"
)
hospital_labeller <- function(variable,value){
  return(hospital_names[as.character(value)])
}

ms <- 1e3

fig17 %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.4) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Variance (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.2, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

fig17 %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=variances_pop*ms, y=variances_opt*ms, color=alg)) +
  geom_point(size=0.8, alpha=0.3) +
  geom_abline(intercept = 0, color="black", alpha=1) +
  labs(x="Obs. variance (ms)", y="Opt. variance (ms)") +
  scale_color_manual("Algorithm:", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = "none") +
  ggtitle("Freq. 8 Hz") +
  theme_classic() -> p2

fig17 %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=errors_pop*ms, y=errors_opt*ms, color=alg)) +
  geom_point(size=0.8, alpha=0.5) +
  lims(x=c(0,25),y=c(0,25)) +
  geom_abline(intercept = 0, color="black", alpha=1) +
  labs(x="Obs. error (ms)", y="Opt. error (ms)") +
  scale_color_manual("Algorithm:", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = "none") +
  ggtitle(" ") +
  theme_classic() -> p3

plot_grid <- rbind(
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, 3, 3),
  c(1, 1, 1, 3, 3),
  c(1, 1, 1, NA, NA))

grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, plot_grid)
```

```{r, fig.width=1.6, fig.height=0.9}

```

```{r, fig.width=1.5, fig.height=0.8}

```
